---
title: "Investment Report"
author: "Thiago"
date: " Last edited `r format(Sys.Date(), '%d %B, %Y')`"
output: 
 html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
   # toc_depth: 2
   # number_sections: true
---
<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
h1.title {
  color: #black;
  background-color: #F5F5F5;
  opacity: 0.6;
  font-family: Calibri;
  font-size: 20px;
}
h4.author {
  color: black;
  font-family: Calibri;
  background-color: #F5F5F5;
}
h4.date {
  color: black;  
  font-family: Calibri;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #F5F5F5;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
}

# pre = code background, TOC = caixa de seleção
</style>
 

```{r setup, include = FALSE}
# This will setup parameters for all chunks on the script
# knitr::opts_chunk$set(fig.align = 'center', out.width = '80%', echo = TRUE)

knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")

investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/78b002735b6f620df7f2767e63b76aaca317bf8d/investment_services_projects.csv")
```


# Datasets 


## Investment Annual Summary
The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each of the following regions for each fiscal year, from 2012 to 2018:

- East Asia and the Pacific      
- Europe and Central Asia        
- Latin America and the Caribbean
- Middle East and North Africa   
- South Asia                     
- Sub-Saharan Afric


1. East Asia and the Pacific      
2. Europe and Central Asia        
3. Latin America and the Caribbean
4. Middle East and North Africa   
5. South Asia                     
6. Sub-Saharan Africa



## Investment Annual Summary

The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each region for each fiscal year, from 2012 to 2018.
```{r investment-annual-summary, out.width = '85%',fig.cap = 'Figure 1.1 The Investment Annual Summary for each region for 2012 to 2018.'}
ggplot(investment_annual_summary, aes(x = fiscal_year, y = dollars_in_millions, color = region)) +
  geom_line() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```



```{r tables}

investment_annual_summary %>%
     count(region, wt = dollars_in_millions) -> investment_region_summary

kable(investment_region_summary, col.names = c("Region", "Dollars in Millions"), align = "cc", caption = "Table 1.1 The total investment summary for each region for the 2012 to 2018 fiscal years.")
```


## Investment Projects in Brazil

The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.
```{r brazil-investment-projects, out.width = '95%',fig.cap = 'Figure 1.2 The Investment Services Projects in Brazil from 2012 to 2018.'}
brazil_investment_projects <- investment_services_projects %>%
  filter(country == "Brazil") 

ggplot(brazil_investment_projects, aes(x = date_disclosed, y = total_ifc_investment_as_approved_by_board_million_usd, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )
```
## Investment Projects in Brazil in 2018







```{r brazil-projects-2018, out.width = '95%',fig.cap = 'Figure 1.3 The Investment Services Projects in Brazil in 2018.'}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= "2017-07-01",
         date_disclosed <= "2018-06-30") 

ggplot(brazil_investment_projects_2018, aes(x = date_disclosed, y = total_ifc_investment_as_approved_by_board_million_usd, color = status)) +
  geom_point() +
  labs(
    title = "Investment Services Projects in Brazil in 2018",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```



## Investment Projects in Brazil in 2018

```{r brazil-investment-projects-2018, out.width = '95%'}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == "Brazil",
         date_disclosed >= "2017-07-01",
         date_disclosed <= "2018-06-30") 

brazil_investment_projects_2018

brazil_investment_projects_2018_total <- brazil_investment_projects_2018 %>%
  summarize(sum_total_investment = sum(total_ifc_investment_as_approved_by_board_million_usd, na.rm = TRUE)) 

brazil_investment_projects_2018_total
```

The total investment amount for all projects in Brazil in the 2018 fiscal year was `r brazil_investment_projects_2018_total` million dollars.


